### 2018-04-24 Risk analysis/Poster/Poster STC 2017/poster_landscape_sfont.tex
Poster update + theses correction

\begin{myblock}{1 - Introduction}
Structural geological modeling is of central importance for the assessment of uncertain hydrocarbon accumulations in potential reservoirs. Hydrocarbon exploration and production is a high-risk, high-reward sector in which good decision making is indispensable.
Utilizing a Bayesian approach, we examine the influence of model uncertainties and respective uncertainty changes on decision making of actors in this field.
%Actors in this field are faced with numerous uncertainties that have to be considered. We examine respective decision making from a Bayesian perspective. 
%...building on recent developments that have transferred this probabilistic approach to address uncertainties in the field of structural geological modeling.
%We examine respective decision making from a Bayesian perspective by considering two main approaches: (1) we treat geological modeling as a Bayesian inference problem, so that additional geological information can be incorporated as likelihood functions linked to prior parameters in a probabilistic framework; (2) we base the decision-making step on value estimation by optimizing a case-specific loss function.

@@

\begin{itemize}
\item The degree of decision convergence can be considered a measure for the state of knowledge and its inherent uncertainty at the moment of decision making.
\item This decisive uncertainty does not change in alignment with model uncertainty but depends on alterations of critical parameters and respective interdependencies.
\item Actors are affected differently by one set of information, depending on their risk affinity.
\item It is important to identify the model parameters which are most influential for the final decision in order to
optimize the decision-making process.
\end{itemize}
These results and conclusions refer to a generic hydrocarbon system case study but are transferable to other fields where decisions
are based on uncertain geological models, for example in hydrogeological or geothermal exploration.
%\vspace{0.3em}
%\begin{figure}
%	\begin{minipage}{0.95\textwidth}
%		\begin{minipage}[t]{0.36\textwidth}
%			\vspace{0pt}
%			\includegraphics[width=\textwidth]{figures/compaction.pdf}
%		\end{minipage}\hfill
%		\begin{minipage}[t]{0.22\textwidth}
%			\vspace{0pt}
%			\caption{
%			Comparison of porosity–depth trend studies and experimental results for shales and
%argillaceous sediments. While for E\&P projects the seal integrity is proven by the abundance of hydrocarbons, for \ce{CO2} storage it remains uncertain. Controlling factors are clay mineral and pore fluid composition, grain sizes, pore pressure and the influence of mechanical \textbf{(MC)} and chemical compaction \textbf{(CC)}. Because core sampling of seal layers is expensive, experimental studies and global databases might be auxiliary. Still, extrapolation of experimental results has limited validity for natural anisotropy and the influence of chemical compaction \citep{mondol_experimental_2007}.
%			} \label{fig:compaction}
%		\end{minipage}\hfill
%		\begin{minipage}[t]{0.38\textwidth}
%			\vspace{0pt}
%			\includegraphics[width=\textwidth]{figures/leakage.pdf}
%			\caption{
%			Different leakage scenarios for a \ce{CO2} storage project which are subject to uncertainty. To prevent a spill out of the storage formation \textbf{(1)}, the storage capacity must be estimated. A break of \ce{CO2} through the formation's roof \textbf{(2)} depends on seal properties and knowledge of fracture pressures (see figure \ref{fig:compaction}). Evaluation of leakage along \textbf{(3)} or through \textbf{(4)} a fault requires the analysis of juxtaposition and smearing. Sub-seismic faults represent an additional risk. Still, the highest risk of leakage exists in close proximity to wells (Figure based on lecture notes, lecture by K. Indrevær \& A. Braathen, 15.6.2017).
%			} \label{fig:leakage}
%		\end{minipage}
%	\end{minipage}
%\end{figure}

>>>>

\begin{myblock}{1 - Introduction}
Structural geological modeling is of central importance for the assessment of uncertain hydrocarbon accumulations in potential reservoirs. Hydrocarbon exploration and production is a high-risk, high-reward sector in which good decision making is indispensable.
Utilizing a Bayesian approach, we examine the influence of model uncertainties and respective uncertainty changes on the decision making of actors in this field.
%Actors in this field are faced with numerous uncertainties that have to be considered. We examine respective decision making from a Bayesian perspective. 
%...building on recent developments that have transferred this probabilistic approach to address uncertainties in the field of structural geological modeling.
%We examine respective decision making from a Bayesian perspective by considering two main approaches: (1) we treat geological modeling as a Bayesian inference problem, so that additional geological information can be incorporated as likelihood functions linked to prior parameters in a probabilistic framework; (2) we base the decision-making step on value estimation by optimizing a case-specific loss function.

@@

\begin{itemize}
\item The degree of \textbf{decision convergence} can be considered a measure for the state of knowledge and its inherent uncertainty at the moment of decision making.
\item This decisive uncertainty does not change in alignment with model uncertainty but depends on alterations of \textbf{critical parameters} and respective interdependencies.
\item Actors are \textbf{affected differently} by one set of information, depending on their risk affinity.
\item It is important to \textbf{identify the model parameters} which are most influential for the final decision in order to
\textbf{optimize the decision-making process}.
\end{itemize}
These results and conclusions refer to a generic hydrocarbon system case study but are transferable to other fields where decisions
are based on uncertain geological models, for example in hydrogeological or geothermal exploration.
%\vspace{0.3em}
%\begin{figure}
%	\begin{minipage}{0.95\textwidth}
%		\begin{minipage}[t]{0.36\textwidth}
%			\vspace{0pt}
%			\includegraphics[width=\textwidth]{figures/compaction.pdf}
%		\end{minipage}\hfill
%		\begin{minipage}[t]{0.22\textwidth}
%			\vspace{0pt}
%			\caption{
%			Comparison of porosity–depth trend studies and experimental results for shales and
%argillaceous sediments. While for E\&P projects the seal integrity is proven by the abundance of hydrocarbons, for \ce{CO2} storage it remains uncertain. Controlling factors are clay mineral and pore fluid composition, grain sizes, pore pressure and the influence of mechanical \textbf{(MC)} and chemical compaction \textbf{(CC)}. Because core sampling of seal layers is expensive, experimental studies and global databases might be auxiliary. Still, extrapolation of experimental results has limited validity for natural anisotropy and the influence of chemical compaction \citep{mondol_experimental_2007}.
%			} \label{fig:compaction}
%		\end{minipage}\hfill
%		\begin{minipage}[t]{0.38\textwidth}
%			\vspace{0pt}
%			\includegraphics[width=\textwidth]{figures/leakage.pdf}
%			\caption{
%			Different leakage scenarios for a \ce{CO2} storage project which are subject to uncertainty. To prevent a spill out of the storage formation \textbf{(1)}, the storage capacity must be estimated. A break of \ce{CO2} through the formation's roof \textbf{(2)} depends on seal properties and knowledge of fracture pressures (see figure \ref{fig:compaction}). Evaluation of leakage along \textbf{(3)} or through \textbf{(4)} a fault requires the analysis of juxtaposition and smearing. Sub-seismic faults represent an additional risk. Still, the highest risk of leakage exists in close proximity to wells (Figure based on lecture notes, lecture by K. Indrevær \& A. Braathen, 15.6.2017).
%			} \label{fig:leakage}
%		\end{minipage}
%	\end{minipage}
%\end{figure}

### 2018-04-24 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Poster update + theses correction

		\subsection{Including different risk affinities in the loss function}		
		It can be assumed that several actors in one sector or decision environment may have the same general loss function but different affinities concerning risks. This might be based for example on different psychological factors or economic philosophies followed by companies. It might also be based on budgets and options such actors have available. An intuitive example is the comparison of a small and a large company. A certain false estimate or error might have a significantly stronger impact on a company which has a a generally lower market share and only few projects, than on a larger company which might possess a higher financial flexibility and for which one project is only one of many development options in a portfolio.\\		
		In the following, the loss function is further adapted to consider different risk affinities of several actors. Representing risk behavior in a loss function can also be done in different ways and regarding different types of risks. Here, bidding lower is considered the cautious, risk-averse option, as smaller losses can be expected from underestimating. Guessing higher is deemed riskier, as losses from overestimation are greater. However, bidding correctly on a higher value, will also return a greater gain. It is assumed that risk-friendly actors care less about fatal underestimation, i.e.\ they will rather develop a project than discard it. In the loss function, risk is simply included using a risk factor \textit{r} which alters the incurred losses respectively:
		\begin{equation}\label{eq:LFR_final}
		L(\theta,\hat{\theta}) =
		\begin{cases}
		|\theta - \hat{\theta}|*r^{-0.5}, & \text{for } 0<\hat{\theta}<\theta  \\
		|\theta-\hat{\theta}|*a*r, & \text{for } 0<\theta<\hat{\theta} \\
		|\theta-\hat{\theta}|*b*r, & \text{for } \theta\leq0<\hat{\theta} \\
		|\theta-\hat{\theta}|*c*r^{-0.5}, & \text{for } \hat{\theta}\leq0<\theta 
		\end{cases},
		\text{ with } a,b,c,r \in \mathbb{Q}.
		\end{equation}	
		\begin{figure}[h]
			\centering
			\includegraphics[width=1\textwidth]{Figures/LFR_normal2.png}
			\caption{Plotting of expected loss realizations after including the risk factor $r$ in the loss function (Equation \ref{eq:LFR_final}) for actors with risk affinities ranging from risk-averse ($r$ = 0.5 and 0.75), over risk-neutral ($r$ = 1), to risk-friendly ($r$ = 1.25 and $r$ = 1.5). The loss function was applied the same normal distribution ($\mu=0; \sigma=500$) as in Figure \ref{fig:LF_4steps_normal}.}\label{fig:LFR_normal} 
		\end{figure}\\
		According to this, for \textit{r} = 1 the risk-neutral loss function is returned, as no re-weighting takes place. For \textit{r} $<$ 1, the weight on overestimating (\textit{a, b}) is reduced and increased for fatal underestimation (\textit{c}), as well as normal underestimation. This represents a risk-friendlier actor that is willing to bid on a higher estimate to attain a greater gain. For \textit{r} $>$ 1, the overestimation weight (\textit{a, b}) is increased in the loss function, underestimation and fatal underestimation weight (\textit{c}) are decreased and respectively more risk-averse actors are prompted to bid on lower estimates. Accordingly different loss function realizations are plotted in Figure \ref{fig:LFR_normal}.\\		
		The factor \textit{r} can take basically any positive values. However, since risk neutrality is expressed by \textit{r} = 1, we consider values 0 $<$ \textit{r} $<$ 2 to be the most appropriate choices to represent both sides of risk affinity equally here.

>>>>

		\subsection{Including different risk affinities in the loss function}		
		It can be assumed that several actors in one sector or decision environment may have the same general loss function but different affinities concerning risks. This might be based for example on different psychological factors or economic philosophies followed by companies. It might also be based on budgets and options such actors have available. An intuitive example is the comparison of a small and a large company. A certain false estimate or error might have a significantly stronger impact on a company which has a a generally lower market share and only few projects, than on a larger company which might possess a higher financial flexibility and for which one project is only one of many development options in a portfolio.\\		
		In the following, the loss function is further adapted to consider different risk affinities of several actors. Representing risk behavior in a loss function can also be done in different ways and regarding different types of risks. Here, bidding lower is considered the cautious, risk-averse option, as smaller losses can be expected from underestimating. Guessing higher is deemed riskier, as losses from overestimation are greater. However, bidding correctly on a higher value, will also return a greater gain. It is assumed that risk-friendly actors care less about fatal underestimation, i.e.\ they will rather develop a project than discard it. In the loss function, risk is simply included using a risk factor \textit{r} which alters the incurred losses respectively:
		\begin{equation}\label{eq:LFR_final}
		L(\theta,\hat{\theta}) =
		\begin{cases}
		|\theta - \hat{\theta}|*r^{-0.5}, & \text{for } 0<\hat{\theta}<\theta  \\
		|\theta-\hat{\theta}|*a*r, & \text{for } 0<\theta<\hat{\theta} \\
		|\theta-\hat{\theta}|*b*r, & \text{for } \theta\leq0<\hat{\theta} \\
		|\theta-\hat{\theta}|*c*r^{-0.5}, & \text{for } \hat{\theta}\leq0<\theta 
		\end{cases},
		\text{ with } a,b,c,r \in \mathbb{Q}.
		\end{equation}	
		\begin{figure}[h]
			\centering
			\includegraphics[width=1\textwidth]{Figures/LFR_normal2.png}
			\caption{Plotting of expected loss realizations after including the risk factor $r$ in the loss function (Equation \ref{eq:LFR_final}) for actors with risk affinities ranging from risk-friendly ($r$ = 0.5 and 0.75), over risk-neutral ($r$ = 1), to risk-averse ($r$ = 1.25 and $r$ = 1.5). The loss function was applied the same normal distribution ($\mu=0; \sigma=500$) as in Figure \ref{fig:LF_4steps_normal}.}\label{fig:LFR_normal} 
		\end{figure}\\
		According to this, for \textit{r} = 1 the risk-neutral loss function is returned, as no re-weighting takes place. For \textit{r} $<$ 1, the weight on overestimating (\textit{a, b}) is reduced and increased for fatal underestimation (\textit{c}), as well as normal underestimation. This represents a risk-friendlier actor that is willing to bid on a higher estimate to attain a greater gain. For \textit{r} $>$ 1, the overestimation weight (\textit{a, b}) is increased in the loss function, underestimation and fatal underestimation weight (\textit{c}) are decreased and respectively more risk-averse actors are prompted to bid on lower estimates. Accordingly different loss function realizations are plotted in Figure \ref{fig:LFR_normal}.\\		
		The factor \textit{r} can take basically any positive values. However, since risk neutrality is expressed by \textit{r} = 1, we consider values 0 $<$ \textit{r} $<$ 2 to be the most appropriate choices to represent both sides of risk affinity equally here.
